Digital Twins for Ocean Robots

### 2024-11-14 paper/paper.tex
fix my name in paper (oups)

\hypersetup{
pdftitle = {Digital Twins for Ocean Robot},
pdfsubject = {JuliaCon 2023 Proceedings},
pdfauthor = {Gaël.Forget},
pdfkeywords = {Julia, Ocean, Robots, Observation, In Situ, Model},
}

>>>>

\hypersetup{
pdftitle = {Digital Twins for Ocean Robot},
pdfsubject = {JuliaCon 2023 Proceedings},
pdfauthor = {Gaël Forget},
pdfkeywords = {Julia, Ocean, Robots, Observation, In Situ, Model},
}
